Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-10 mtjournal.tex
moved section on mean-removal to paradigm, added labels

% override ulem 's default change of \emph{} -- remove before ship
\normalem
\section{Introduction}

@@

\textbf{JGK: I think the next paragraph belongs elsewhere}
\begin{itemize}
\item \sout{one challenge of metric-evaluation: underlying doc difficulty }
  \begin{itemize}
  \item \sout{describe mean-subtraction}
  \end{itemize}
\end{itemize}
When considering a candidate measure $m$, reporting correlations of
$m$ with absolute HTER scores can conflate $m$'s power in identifying
which of two candidate translations is better with $m$'s (and HTER)'s
ability to distinguish which of two source documents is more difficult
to translate. To avoid this conflation, we consider the mean-removed
$m$ and HTER scores; this lowers the correlations but ensures that the
reported correlations are among differences in the translations rather
than among differences in the underlying document.

\section{Approach}

@@

\end{itemize}
\section{Experimental paradigm}

@@

\item Implementation
  \begin{itemize}
  \item Charniak parser
  \item n=1..50
  \item head-finding, with some modifications
  \item label-construction
  \end{itemize}
\end{itemize}

\section{Correlation with human judgments of fluency \& adequacy}

Corpus: LDC Multiple Translation Chinese corpus 3\&4 treat each
segment and each judgment as independent data point

@@

\section{Correlations with HTER}

  Corpus
    Gale translation corpus 2.5; 3 sites, 2 source languages, 4 genres each

@@

\section{Weight-tuning to combine syntax and other knowledge sources}

@@

\section{Conclusion}

expected dependency pair matching gets at something new

>>>>

% override ulem 's default change of \emph{} -- remove before ship
\normalem
\section{Introduction}
\label{sec:intro}

@@

\section{Approach}
\label{sec:approach}

@@

\end{itemize}
\section{Experimental paradigm}
\label{sec:paradigm}

@@

\item Implementation
  \begin{itemize}
  \item Charniak parser
  \item n=1..50
  \item head-finding, with some modifications
  \item label-construction
  \end{itemize}

\begin{itemize}
\item \sout{one challenge of metric-evaluation: underlying doc difficulty }
  \begin{itemize}
  \item \sout{describe mean-subtraction}
  \end{itemize}
\end{itemize}
When considering a candidate measure $m$, reporting correlations of
$m$ with absolute HTER scores can conflate $m$'s power in identifying
which of two candidate translations is better with $m$'s (and HTER)'s
ability to distinguish which of two source documents is more difficult
to translate. To avoid this conflation, we consider the mean-removed
$m$ and HTER scores; this lowers the correlations but ensures that the
reported correlations are among differences in the translations rather
than among differences in the underlying document.

\section{Correlation with human judgments of fluency \& adequacy}
\label{sec:faexpts}
Corpus: LDC Multiple Translation Chinese corpus 3\&4 treat each
segment and each judgment as independent data point

@@

\section{Correlations with HTER}
\label{sec:hter1}
  Corpus
    Gale translation corpus 2.5; 3 sites, 2 source languages, 4 genres each

@@

\section{Weight-tuning to combine syntax and other knowledge sources}
\label{sec:hter2}

@@

\section{Conclusion}
\label{sec:conclusion}
expected dependency pair matching gets at something new
